Boolean Operations on Surfaces in VTK Without External Libraries

### 2011-05-18 Document/LaTeX/Article.tex
Changed the handle number to the correct one.
Updated the document to reflect the latest changes.

% 
% NOTE: This is the last number of the "handle" URL that 
% The Insight Journal assigns to your paper as part of the
% submission process. Please replace the number "1338" with
% the actual handle number that you get assigned.
%
\newcommand{\IJhandlerIDnumber}{1338}

% Increment the release number whenever significant changes are made.
% The author and/or editor can define 'significant' however they like.
\release{1.00}

@@

To support distance-based boolean operations, we introduce another class, \code{vtkPolyDataDistance}, that computes the distance from points in the first input \code{vtkPolyData} to a second by evaluating the signed distance field from the second input using the \code{vtkImplicitPolyData} class. Optionally, the distance from points in the second input \code{vtkPolyData} to the first can also be computed. These distances are stored as a point data field named ``Distance''.

@@

There are two ways to use the classes we have developed to compute the surface mesh resulting from a boolean operation on two surface meshes: setting up a VTK pipeline or using a new class \code{vtkPolyDataBooleanOperationFilter}.

@@

To compute a surface resulting from a boolean operation on surface meshes, the pipeline of classes shown in Figure \ref{fig:Pipeline} can be used to compute the desired surface. The two arrows between \code{vtkPolyDataIntersection} and \code{vtkPolyDataDistance} indicate that the two output surfaces from \code{vtkPolyDataIntersection} are set as the input to \code{vtkPolyDataDistance}. The two instances of \code{vtkThreshold} operate on different outputs of \code{vtkPolyDataDistance}.

@@

\subsection{vtkPolyDataBooleanOperationFilter}

For convenience, we have included a single class that replicates the functionality  class for computing boolean operations on surface meshes, \code{vtkPolyDataBooleanOperationFilter}, that encapsulates the functionality of the pipeline above. This class has three options. The desired boolean operation is specified with one of
\begin{verbatim}
void SetOperationToUnion();
void SetOperationToIntersection();
void SetOperationToDifference();
void SetOperation(int operation);
\end{verbatim}
The default operation is union.

@@

Lastly, the \code{Tolerance} sets a threshold on the absolute value of a distance field value below which the distance is considered to be zero.
\section{Results}

>>>>

% 
% NOTE: This is the last number of the "handle" URL that 
% The Insight Journal assigns to your paper as part of the
% submission process. Please replace the number "1338" with
% the actual handle number that you get assigned.
%
\newcommand{\IJhandlerIDnumber}{3262}

% Increment the release number whenever significant changes are made.
% The author and/or editor can define 'significant' however they like.
\release{2.00}

@@

To support distance-based boolean operations, we introduce another class, \code{vtkPolyDataDistance}, that computes the distance from points in the first input \code{vtkPolyData} to a second by evaluating the signed distance field from the second input using the \code{vtkImplicitPolyData} class. Optionally, the distance from points in the second input \code{vtkPolyData} to the first can also be computed. These distances are stored as a point data field named ``Distance''. In addition, the filter computes a cell data field named ``Distance'' that contains the distance from the center of each cell to the nearest point on the second input

@@

There are two ways to use the classes we have developed to compute the surface mesh resulting from a boolean operation on two surface meshes: setting up a VTK pipeline or using a new class \code{vtkBooleanOperationPolyDataFilter}.

@@

To compute a surface resulting from a boolean operation on surface meshes, the pipeline of classes shown in Figure \ref{fig:Pipeline} can be used to compute the desired surface. The two arrows between \code{vtkPolyDataIntersection} and \code{vtkPolyDataDistance} indicate that the two output surfaces from \code{vtkPolyDataIntersection} are set as the input to \code{vtkPolyDataDistance}. The two instances of \code{vtkThreshold} operate on the two outputs of \code{vtkPolyDataDistance}. The example \verb+PipelineExample.cxx+ included with the source code in this article shows how to set up a pipeline to compute boolean operations.

@@

\subsection{vtkBooleanOperationPolyDataFilter}

For convenience, we have included a single class that replicates the functionality  class for computing boolean operations on surface meshes, \code{vtkBooleanOperationPolyDataFilter}, that encapsulates the functionality of the pipeline above. This class has three options. The desired boolean operation is specified with one of
\begin{verbatim}
void SetOperationToUnion();
void SetOperationToIntersection();
void SetOperationToDifference();
void SetOperation(int operation);
\end{verbatim}
The default operation is union.

@@

Lastly, the \code{Tolerance} sets a threshold on the absolute value of a distance field value below which the distance is considered to be zero.

An example in the file \verb+BooleanOperationPolyDataFilterExample.cxx+ is included in the source code for this article.

\section{Results}
